On exponential sums arising from the classical doubling method

### 2025-04-02 main.tex
Adjustments for the unitary case :(

Given a character $$\theta = \prod_{j=1}^{\lengthof(\lambda^+)} \alpha_j \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta_i \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex},$$ we choose a torus of $T'$ of $\GL_{2 \left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor}\left(\quadraticExtension\right)$ of the form $$T' \cong \prod_{j=1}^{\lengthof(\lambda^+)} \left(\multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}} \times \multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}}\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}}$$ and define a character $\theta' \colon T' \to \multiplicativegroup{\cComplex}$ by the formula
$$\theta' = \prod_{j=1}^{\lengthof(\lambda^+)} \left(\alpha_j \times \minusInvolution{\alpha}_j\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta'_j,$$
where we recall that $\theta'_j \colon \multiplicativegroup{\finiteFieldExtension{2 \lambda_j^{-}}} \to \multiplicativegroup{\cComplex}$ is given by $$\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{\lambda_j^-}}\right).$$

>>>>

Given a character $$\theta = \prod_{j=1}^{\lengthof(\lambda^+)} \alpha_j \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta_i \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex},$$ we choose a torus of $T'$ of $\GL_{\frac{2}{\grpIndex{\quadraticExtension}{\finiteField}} \left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor}\left(\quadraticExtension\right)$ of the form $$T' \cong \prod_{j=1}^{\lengthof(\lambda^+)} \left(\multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}} \times \multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}}\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}}$$ and define a character $\theta' \colon T' \to \multiplicativegroup{\cComplex}$ by the formula
$$\theta' = \prod_{j=1}^{\lengthof(\lambda^+)} \left(\alpha_j \times \minusInvolution{\alpha}_j\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta'_j,$$
where we recall that $\theta'_j \colon \multiplicativegroup{\finiteFieldExtension{2 \lambda_j^{-}}} \to \multiplicativegroup{\cComplex}$ is given by $$\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{\lambda_j^-}}\right).$$
